---
title: "SQL Exercise"
author: "Yonatan Vishenko"
format: html
editor: visual
toc: True
---

## setting up the db:

```{r}
con_chocolate <- DBI::dbConnect(drv = RSQLite::SQLite(),
dbname = "chocolate.sqlite")

```

## Question 1:

1.  The query asks for the Names of the salesreps and their total amount of candy bars sold in the year 2022. The and result should be a table containing the columns:

    -   Name: The names of all the salesreps who joined during 2010
    -   total_candy_bars_sold: The sum of all the candy bars each of these salesreps sold throughout 2022. The query uses INNER JOIN to match the names of the salesreps from the table 'salesreps' and the amount of candy they sold from the table 'orders'.

2.  

```{sql,connection = con_chocolate, output.var = "q_1_df"}
SELECT salesreps.Name, SUM(orders.amount) AS total_candy_bars_sold
FROM salesreps INNER JOIN orders USING (srid)
WHERE
orders.sale_date BETWEEN '2022-01-01' AND '2022-12-31'
AND salesreps.year_joined = 2010
GROUP BY salesreps.Name;
```

```{r}
q_1_df
```

There are three salesreps that joind in 2010;

In 2022 Tootle, Naudia sold 1825, al-Farrah, Ghaaliba sold 1866 and al-Sadri, Saamyya sold 1784 candy bars.

## Question 2:

```{sql,connection = con_chocolate, output.var = "q_2_df"}
SELECT DISTINCT count(cid) AS total_orders,
                count(cid) OVER (PARTITION BY count(cid)) AS N
FROM orders
GROUP BY cid
ORDER BY total_orders

```

## Question 3:

```{sql, connection = con_chocolate, output.var = "q_3_df"}
SELECT salesreps.Name, products.candy_names
FROM orders INNER JOIN products USING(pid)
INNER JOIN salesreps ON orders.srid = salesreps.srid
WHERE orders.sale_date BETWEEN '2022-04-01' AND '2022-06-30' 
      AND orders.pid IN
      (select pid
      FROM orders 
      WHERE sale_date BETWEEN '2022-01-01' AND '2022-03-31'
      GROUP BY pid
      order by sum(amount) desc
      limit(1))
GROUP BY orders.srid
ORDER BY sum(orders.amount) DESC
LIMIT(1)
```

```{r}
q_3_df
```

The candy bar with the highest number of total orders in the first quarter of 2022 is 'Coconut Crave'. And the name of the sales rep that sold the most of those candy bars in the second quarter of 2022 is 'Hess, Christopher'.
